---
title: "p8105_hw4_mz2662"
author: "Mengqi Zhu"
date: "2017-10-27"
output: html_document
---


```{r message=FALSE,warning=FALSE}
library(tidyverse)
library(janitor)
library(readxl)
```

For Problem1, Weijie Liu(UNI: wl2632) is my collaborator.

# Problem 1
```{r message=FALSE,warning=FALSE}
pups_data = read_csv("./data_import_examples/FAS_pups.csv", col_types = "ciiiii") %>% 
  clean_names() %>% 
  mutate(sex = recode(sex, `1` = "male", `2` = "female"))

pups_tidy_data = gather(pups_data, key = PD_outcome, value = days, pd_ears: pd_walk) %>% 
  na.omit()
```

```{r message=FALSE,warning=FALSE}
library(ggridges)
library(ggthemes)
pups_tidy_data %>%
  ggplot(aes(x = days, y = PD_outcome, color = PD_outcome)) +
  geom_density_ridges(scale = .75)
```

Comments:
We can see from the plot that the landmarks occur in the sequence of: ears, pivot, walk, eyes. The post-natal days of ears are centralized around 3-5 days, the post-natal days of pivot are centralized around 5-8 days, the post-natal days of walk are centralized around 8-11 days, the post-natal days of eyes are centralized around 12-14 days.

The GitHub repo containing our solution to this problem is https://github.com/WendyThe13th/RMD.